Supporting Ecological Decision Making Using Feature-Selection and Variable Importance

### 2019-09-02 code/98-paper/ieee/ieee-manuscript.tex
update results: performance

%%%% using 'arara' 4.0
% arara: pdflatex: {synctex: yes, interaction: nonstopmode}
% arara: bibtex
%% arara: latexindent
% arara: pdflatex: {synctex: yes, interaction: nonstopmode}
% arara: pdflatex: {synctex: yes, interaction: nonstopmode}

@@

% filters
% - influence varies based on algorithm
% - no substantial improvement on these datasets compared to no filter
% - no substantial descrese in performance
% - no advantage of ensemble borda filter compared to others
Differences between filter methods were neglibly small in this study.
Ensemble filters showed no substantial difference to simple filter methods.
However, there was also no change to worse when using filter methods compared to using none.
Comparing absolute values, filters "Carscore", "Information gain" and the "Borda" ensemble filter scored the best results across all learners and tasks.

\input{performance-top-20}

\input{performance-best-per-learner.tex}

@@

>>>>

%%%% using 'arara' 4.0
% arara: pdflatex: {synctex: yes, interaction: nonstopmode}
% arara: bibtex
% arara: latexindent
% arara: pdflatex: {synctex: yes, interaction: nonstopmode}
% arara: pdflatex: {synctex: yes, interaction: nonstopmode}

@@

% filters
% - influence varies based on algorithm and task (SVM very small influence, RF medium, XGB medium)
% - no substantial descrease in performance when using filters
% - no advantage of ensemble borda filter compared to others
Effects of filter methods on performance differed between algorithms:
With the expection of one or two methods, SVM showed a constant performance of all filters across tasks (\autoref{fig:filter-perf-all}).
RF showed a normal distribution for most tasks with one or two different methods taking the lead on each task.
For RF, filter "Carscore" showed the best performance in three out of six tasks while this was achieved for XGBoost by filter "CMIM".
XGBoost showed a diverse distribution with less clustering of filters as SVM and RF (referring to RMSE).

% filter vs no filter
When comparing the usage of filters vs using no filter at all, there was only one instance (XGBoost on the HR-NRI task) when the model with no filtering showed a slighly better performance than the best filtered one (\autoref{fig:filter-effects}).
In general, the effect of filtering vs. no filtering differed without a clear pattern across tasks: For example, SVM and RF showed a substantial increase for the NRI task when filtering the data while there was almost no effect for XGBoost (\autoref{fig:filter-effects}).
For task HR, there was a medium effect of applying filtering for RF, almost none for SVM and a large one for XGBoost.

% latex table top 20 absolute performances
\input{performance-top-20}

% latex table best performance per learner
\input{performance-best-per-learner.tex}

@@

% plot no filter vs best filter for each model and task
\begin{figure} [t!]
\centering
	\begin{center}
		\includegraphics[width=0.5\textwidth] {filter-effect-1.pdf}
        \caption{Model performances in RMSE when using no filter method compared to the best scoring filter method for each learner across all tasks.}
		\label{fig:filter-effects}
	\end{center}
\end{figure}
\subsection{Permutation-based variable importance}

% plot no filter vs best filter for each model and task
\begin{figure} [t!]
\centering
	\begin{center}
		\includegraphics[width=0.5\textwidth] {filter-perf-all-1.pdf}
        \caption{Model performances in RMSE of all used filter methods and PCA for each learner across all tasks.}
		\label{fig:filter-perf-all}
	\end{center}
\end{figure}
